Social Computing Article\thanks{This title is temporary}

### 2013-01-14 Article.tex
Escrevi um pouco nos resultados

Human beings are known to be able to easily perform tasks which are still generally difficult for computers, such as natural language processing and image recognition. However, it would be useful to be able to apply human social computation to more straightforward computer problems with precise definitions and algorithms, but which are still computationally intensive. The different sets of abilities between computers and humans suggest that the latter might provide a new approach to those problems that might be more effective than current techniques employed by computers. That notion has been successfully applied, for example, in one of the most significant problems in the field of bioinformatics: protein structure prediction (PSP). A software that presents the problem to humans as an online computer game, called \emph{Foldit} \cite{cooper:foldit}, has produced significant results in the research of PSP, which is usually approached as an optimization problem requiring extensive computational power. Those results have been attributed to human visual problem-solving and decision-making abilities, as well as social collaboration \cite{cooper:foldit}. However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional techniques. To take full advantage of human problem-solving strategies, we must learn their limitations. In order to obtain that knowledge, our system simulates human behaviour according to findings of social computation experiments.

@@

The origin of human computation as we know it today can be traced back to the work of \cite{vonahm:gwap}, which identified the possibility of using entertainment as an incentive to participation of human subjects, applying it in games in which the participants are actually performing a computation. That is an idea that also appears in the Foldit game.

The series of experiments summarized in \cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems. The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal.

Other initiatives have appeared, such as the ones by \cite{farenzena:collabem} and \cite{mason:collablearnet}, which take a different approach by having subjects trying to solve the collective problem individually, with the possibility of exchanging solutions between neighbours. Those have resulted in interesting conclusions on human behaviour when the possibility of copying peers makes itself present. It's in those models of experiments that we will focus in this work.

The experiments conducted by \cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT) and the popular \emph{Sudoku} game, with individuals connected through the network being able to exchange partial solutions of the problem in question. There were two main patterns of behaviour observed in this study in regard to copying neighbours' solutions:

\begin{itemize}
	\item Humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one. On the other hand, \cite{mason:collablearnet} suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that wasn't provided.
	\item There is a higher probability of individuals copying peers' solutions when those are shared by several neighbours. That behaviour is referred to by the authors as \emph{conformism}. A similar behaviour was observed by \cite{mason:collablearnet}, even though the experiments used a different problem.
\end{itemize}

\cite{mason:collablearnet} also provided important insights to human cooperation. However, since our basis is the work of \cite{farenzena:collabem} we will use the former's results only as secondary support.

@@

We have built a multi-agent system that simulates the experiments of \cite{farenzena:collabem}, using the model of human behaviour proposed by them. We adapted that behaviour into a set of rules which we modeled in the \emph{Memetic Network} model proposed by \cite{araujo:memenet}. For simplicity, we limited our experiments to the Sudoku problem. Our goal is verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.

@@

>>>>

Human beings are known to be able to easily perform tasks which are still generally difficult for computers, such as natural language processing and image recognition. However, it would be useful to be able to apply human social computation to more straightforward computer problems with precise definitions and algorithms, but which are still computationally intensive. The different sets of abilities between computers and humans suggest that the latter might provide a new approach to those problems that might be more effective than current techniques employed by computers. That notion has been successfully applied, for example, in one of the most significant problems in the field of bioinformatics: protein structure prediction (PSP). A software that presents the problem to humans as an online computer game, called \emph{Foldit}~\cite{cooper:foldit}, has produced significant results in the research of PSP, which is usually approached as an optimization problem requiring extensive computational power. Those results have been attributed to human visual problem-solving and decision-making abilities, as well as social collaboration~\cite{cooper:foldit}. However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional techniques. To take full advantage of human problem-solving strategies, we must learn their limitations. In order to obtain that knowledge, our system simulates human behaviour according to findings of social computation experiments.

@@

The origin of human computation as we know it today can be traced back to the work of~\cite{vonahm:gwap}, which identified the possibility of using entertainment as an incentive to participation of human subjects, applying it in games in which the participants are actually performing a computation. That is an idea that also appears in the Foldit game.

The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems. The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal.

Other initiatives have appeared, such as the ones by~\cite{farenzena:collabem} and~\cite{mason:collablearnet}, which take a different approach by having subjects trying to solve the collective problem individually, with the possibility of exchanging solutions between neighbours. Those have resulted in interesting conclusions on human behaviour when the possibility of copying peers makes itself present. It's in those models of experiments that we will focus in this work.

The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT) and the popular \emph{Sudoku} game, with individuals connected through the network being able to exchange partial solutions of the problem in question. There were two main patterns of behaviour observed in this study in regard to copying neighbours' solutions:

\begin{itemize}
	\item Humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one. On the other hand,~\cite{mason:collablearnet} suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that wasn't provided.
	\item There is a higher probability of individuals copying peers' solutions when those are shared by several neighbours. That behaviour is referred to by the authors as \emph{conformism}. A similar behaviour was observed by~\cite{mason:collablearnet}, even though the experiments used a different problem.
\end{itemize}

\cite{mason:collablearnet} also provided important insights to human cooperation. However, since our basis is the work of~\cite{farenzena:collabem} we will use the former's results only as secondary support.

@@

We have built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. We adapted that behaviour into a set of rules which we modeled in the \emph{Memetic Network} model proposed by~\cite{araujo:memenet}. For simplicity, we limited our experiments to the Sudoku problem. Our goal is verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.

@@

\subsection{Evaluating the neighbours' solutions is beneficial}

Of the three metric employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours. The other chose who to copy based on position, simulating observed human behaviour, and the remaining one chose a neighbour randomly. Our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy. In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution. That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them.
